\documentclass[10pt]{article}
%\usepackage{kpfonts,baskervald}
%\usepackage{inter} \sffamily
\usepackage[a4paper,
            %showframe,
            margin={1cm, 1cm, 1cm, 1cm}]{geometry}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}

\definecolor{myseablue}{rgb}{0.0706, 0.1490, 0.2784}
\definecolor{mylightblue}{rgb}{0.4000, 0.6078, 0.7373}
\definecolor{mywiteish}{rgb}{0.9922, 0.9412, 0.8353}
\definecolor{myred}{rgb}{0.7569, 0.0706, 0.1216}
\definecolor{mydarkred}{rgb}{0.4706, 0.0000, 0.0000}
\definecolor{myblue}{rgb}{0.157, 0.294, 0.388}
\definecolor{mygray}{rgb}{0.0, 0.0, 0.0}
\definecolor{myblueish}{rgb}{0.235, 0.431, 0.443}

\usepackage{enumitem}
\setlength{\parindent}{0pt}
\setlist[itemize]{
    itemsep = 0em,
    parsep = 0em,
    topsep = 0em,
    leftmargin = 1.5em,
}

\newcommand{\horizline}{\vspace{0.4em}\hrule height 0.6pt \vspace{0.4em}}
\newcommand{\shorthorizline}{\centerline{\rule{0.5\textwidth}{0.1pt}}}

\newcommand{\sezione}[1]{
    \vspace{1em}{\large{\textsc{#1}}}
    \horizline
}

\newcommand{\period}[1]{\textit{#1}}
\newcommand{\place}[1]{{#1}}
\newcommand{\uni}[1]{
    \vspace{0.5em}
    \textbf{#1}
}
\newcommand{\details}[1]{\textsl{#1}}
\newcommand{\degree}[1]{\textsl{#1}}

\newcommand{\hrefico}[2]{{%\color{myblue}
\href{#1} {#2 {\footnotesize \ico{external-link-alt}}}}}

\newcommand{\ico}[1]{{\footnotesize \faIcon[regular]{#1}}}

% --- %

\title{curriculum_vitae}
\author{Giacomo Lorenzon}

\begin{document}\pagestyle{empty}

{
\renewcommand{\arraystretch}{1.3}
% Intestazione
\begin{tabularx}{\textwidth}{X r}
     \LARGE \textsc{Giacomo Lorenzon} & Milan, Italy \\ 
     \hline
     \href{mailto:lorenzon.giacomo99@gmail.com}{\ico{envelope} lorenzon.giacomo99@gmail.com},  
     \href{https://github.com/GiacomoLorenzon}{\ico{github} github}, 
     \href{https://giacomolorenzon.github.io/portfolio/}{\ico{link} personal page} 
     & \raggedleft \ico{phone-alt} +39 347 254 8166
\end{tabularx}
}

\sezione{Education}
\vspace{-0.5em}
\uni{Polytechnic University of Milan.} \place{Milan, Italy}. \period{Spring 2025 -- ongoing}.\\
\degree{PhD in Mathematical Models and Methods in Engineering}.\\
GPA 30/30. Supervisor: Prof. F. Regazzoni.
\begin{itemize}
    \item Research focus: \textit{Geometric and Probabilistic Methods for Uncertainty Quantification in Machine Learning}.
\end{itemize}


\uni{Polytechnic University of Milan.} \place{Milan, Italy}. \period{Fall 2021 -- Spring 2024}.\\
\degree{Master of Science in 
Mathematical Engineering: 
Computational Science and Computational Learning}.\\
GPA 29.2/30. Final grade: 110/110 cum Laude.
\vspace{0.3em}
{\color{mygray}
\begin{itemize}

\item Master thesis: 
%``\textit{A discontinuous Galerkin approach for the heterodimer model}''. Supervision of Prof.ssa P. Antonietti.
``A discontinuous Galerkin approach for the heterodimer model of prion dynamics'', under the supervision of Prof.ssa P. Antonietti, head of the Math Dept.

\item Relevant coursework: Stochastic Dynamical Models; Algorithms and Parallel Computing; Advanced Programming for Scientific Computing; Advanced PDEs; Real and Functional Analysis; Numerical Analysis for Partial Differential Equations; Graph Optimisation; Computational Fluid Dynamics.
\end{itemize}
}


\uni{Sorbonne University, Pierre et Marie Curie.} \place{Paris, France}. \period{Fall 2022 -- Spring 2023}.\\
\degree{Exchange program at the Departments of Mathematics and Computational Mechanics}.
{\color{mygray}
\begin{itemize}
\item Advanced numerical methods for continuum models; foundation of non-linear dynamics.
\end{itemize}
}


\uni{Polytechnic University of Milan.} \place{Milan, Italy}. \period{Fall 2018 -- Fall 2021}.\\
\degree{Bachelor of Science in Mathematical Engineering}.
{\color{mygray}
\begin{itemize}
\item Core training in Analysis, Probability, Statistics, Numerical Methods, and Optimisation.
\end{itemize}
}

\sezione{Research activity}

{\color{mygray}
\begin{itemize}

    \item \textbf{High-performance numerical methods for PDEs.} 
    Design of MPI-parallel solvers for reduced fluid–structure models and development of domain-decomposed DG schemes, with theoretical and computational validation.

    \item \textbf{Computational modelling in neuroscience (BraiNum project).} 
    Mathematical modelling and construction of computational solvers for neurodegenerative processes arising from prion-like propagation.

    \item \textbf{Scientific computing and cardiac modelling (life$^x$ project).} 
    Contributions to a C++ high-performance FEM framework for large-scale physiological simulations: 
    parallelisation strategies, solver optimisation, and benchmarking.

    \item \textbf{Publication.} 
    P.~F.~Antonietti, M.~Corti, G.~Lorenzon. 
    \hrefico{https://www.arxiv.org/abs/2407.16065}{\textit{A discontinuous Galerkin method for the three-dimensional heterodimer model with application to prion-like proteins' dynamics}}. 
    In: Proceedings of the European Congress of Mathematics (2024).

    \item \textbf{Ongoing research.} 
    Probabilistic methods for machine learning, uncertainty quantification, and stochastic dynamics; 
    analysis of high-dimensional energy landscapes in spin-glass inspired models and applications to epistemic uncertainty.

\end{itemize}
}


\sezione{Languages and Competences}
\vspace{-1em}
{\color{mygray}
\begin{description}[itemsep=0pt, parsep=0pt, leftmargin=0em]
    \item[\textbf{Languages}] Italian (native), English, French.
    
    \item[\textbf{Mathematics}] 
    Probability and stochastic processes; optimisation; variational inference; 
    stochastic dynamics and Langevin-type methods; high-dimensional statistical modelling.

    \item[\textbf{Programming}] 
    C, C++17/20 (MPI, OpenMP), Python (NumPy, JAX), 
    MATLAB, R; Bash and Linux environments.

    \item[\textbf{Machine Learning \& UQ}] 
    Deep learning, generative modelling (flow matching, SDE-based models), 
    Bayesian inference, uncertainty quantification, spin-glass inspired models.

    \item[\textbf{High-Performance Computing}] 
    Parallel solver design; performance optimisation; HPC clusters, Git (CI/CD), Docker.
\end{description}
}

\vspace{-0.5em}
\sezione{Selected Recognitions}
{\color{mygray}
\begin{itemize}

    \item Merit-based scholarships from INPS and Lombardy Region for academic excellence (2022, 2024, 2025).

    \item Polytechnic University of Milan scholarship for high-merit students (2020, 2021, 2022).

    \item National Excellence Honor Roll (MIUR) and Medal for academic distinction (2019).

    \item \emph{Alfieri del Lavoro} nominee, Presidential acknowledgement for outstanding high-school achievements (2017).
\end{itemize}
}

\sezione{Relevant experiences}
% FIN
% \textbf{Starting finance PoliMi} \details{Active member} - \place{Politecnico} \period{2018-2023}.\\
\textbf{JPMorgan Chase \& Co.} \details{Quantitative Research} - Focused on quantitative methods to estimate default probability.\\
%\textbf{Banca Generali - Reply} \details{Virtual portfolio risk management} - Investment challenge.\\% \place{Milan}, \period{2021}.\\
% GEN
\textbf{Gallarate Basketball team} \details{Playmaker, Captain} - Leadership and coordination responsibilities.\\ % \place{Gallarate, Italy } \period{2008 -- 2019}.\\
\textbf{Model United Nations} \details{School leader} - UN simulation in the Economic and Financial Committee with structured debate. % Merit-based participation at the simulation of a UN session as ``Ambassador of Greece, Economic and Financial Committee''. \place{Athens, Greece } \period{2015}.
% \textbf{Volandia Park and Museum of Flight} \details{Project leader} - Development of the museum's website. \place{Milan, Italy } \period{2017}.
\textbf{PoliMi Sailing Team} - Performance Department: turbulence modelling on hydrofoils.

\sezione{Volunteering and Interests}
\begin{tabular}{l l}
    \textbf{Volunteering}
    &Educational help to children with learning difficulties at ASA. \place{Gallarate, Italy}. \period{2014 -- 2020}.\\
    &Blood donor at AVIS. \place{Gallarate, Italy}. \period{2017 -- present}.\\
    \textbf{Interests}
    &Piano, Saxophone, Philosophy, Basketball, Tennis, Skiing, Alpinism, Climbing, Mathlete.
\end{tabular}
\end{document}
